Title

### 2022-12-15 Manuscript/Manuscript.Rmd
editing method

---
title: "Title"
date: '2022-10-26'
output: 
  pdf_document :
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \usepackage{caption}
 \renewcommand{\caption}{Figure}

@@

3. The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness. However, we found a strong positive relationship between richness and asynchrony of pollinators. As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate. However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.

@@

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984]. Among main driving of stability are the diversity and species asynchrony. A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019]. The stability is also influenced by the degree of asynchrony between species. In this sense, higher levels of asynchrony in species fluctuation stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018]. It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness [@Bluthgen2016; @Valencia2020]. While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.

@@

[?](Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al. 2004; Burd 1994; Knight et al. 2005).plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al. 2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012))

In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and asynchrony of pollinator species as drivers of stability of visitation rate. We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities. In addition, we analyzed whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies over time.

[Hipotesis]()

@@

For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites and a minimum of two years per site. The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999. To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot. To calculate synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018). All of them were positively correlated to each other within each plant species [sup mat?](), therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses. This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous. Finally, we express asynchrony as 1-Loreau and de Mazancourt’s index of synchrony.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

>>>>

---
title: "Title"
date: '2022-10-26'
output: 
  pdf_document :
    latex_engine : xelatex
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \usepackage{caption}
 \renewcommand{\caption}{Figure}

@@

3. The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness. Likewise, we found a strong positive relationship between richness and asynchrony of pollinators. As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate. However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.

@@

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984]. Among main driving of stability are the diversity and species asynchrony. A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019]. The stability is also influenced by the degree of asynchrony between species. In this sense, higher levels of asynchrony in species fluctuation stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018]. It has been also shown that stability can associate more strongly with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Valencia2020]. While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.

@@

In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and asynchrony of pollinator species as drivers of stability of visitation rate. We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities. In addition, we analyzed whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies over time. We expect that the stability of visitation rate will increase with higher richness and asynchrony of pollinators. In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.

@@

For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites and a minimum of two years per site. The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999. To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot. [The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:](al final he puesto que utilizamos este solo porque al corregir el esfuerzo de muestreo este y el de Gross ya no estan correlacionados. He analizado el de Gross y no hay relacion con la estabilidad de las visitas. Muchos trabajos que solo utilizan un indice no dicen que hayan probado otros como es el trabajo de Lazaro, y he visto que muchos ponen la ecuacion, si no te parece bien asi vuelvo a poner los tres y explico lo de la correlacion)

$$
\begingroup\Large
\phi =\frac{\sigma_{x_T}^2}{(\sum\sigma_{x_T})^2}
\endgroup
$$
where ${\sigma_{x_T}^2}$ represents the temporal variance of the community times series and ${(\sum\sigma_{x_T})^2}$ represents the sum of the temporal standard deviation of the time series across all species. This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous. Finally, we express asynchrony as $1-\phi$.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.
